|

### 2021-09-20 paper.Rmd
plot width

# actual plotting
ggplot(pdata_neutral_correction, aes(x = outcome, y = estimate, color = correction, shape = correction)) +
  geom_point(size = 1.5, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, linetype = emotion),
                size = 0.5,
                width = 0.5,
                position = position_dodge(width = 0.5)) +
  geom_hline(yintercept = 0, linetype = 3) +
  ylim(c(-0.2, 0.2)) +
  labs(x = "",
       y = "") +
  facet_wrap(fct_rev(emotion) ~ fct_rev(type), scales = "free") +
  coord_flip() +
  #scale_colour_manual(values = c("grey25", "grey50", "grey75")) +
  scale_color_viridis_d(begin = 0, end = 0.5, direction = -1) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  scale_shape_manual(values = c(17, 16)) +
  theme_nice() +   
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.key.size = unit(1, 'cm'),
        strip.text.x = element_text(size = 8)
    ) +
  guides(color = guide_legend(reverse = TRUE),
         linetype = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

@@

# actual plot
ggplot(pdata_counter_frame, aes(x = outcome, y = estimate, color = correction, shape = correction)) +
  geom_point(size = 1.5, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, linetype = emotion),
                size = 0.5,
                width = 0.5,
                position = position_dodge(width = 0.5)) +
  geom_hline(yintercept = 0, linetype = 3) +
  ylim(c(-0.2, 0.2)) +
  labs(x = "",
       y = "") +
  facet_wrap(fct_rev(emotion) ~ fct_rev(type), scales = "free") +
  coord_flip() +
  #scale_colour_manual(values = c("grey25", "grey50", "grey75")) +
  scale_color_viridis_d(begin = 0, end = 0.75, direction = -1) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  scale_shape_manual(values = c(15, 16)) +
  theme_nice() +   
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.key.size = unit(1, 'cm'),
        strip.text.x = element_text(size = 8)
  ) +
  guides(color = guide_legend(reverse = TRUE),
         linetype = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

>>>>

# actual plotting
ggplot(pdata_neutral_correction, aes(x = outcome, y = estimate, color = correction, shape = correction)) +
  geom_point(size = 1.5, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, linetype = emotion),
                size = 0.5,
                width = 0.25,
                position = position_dodge(width = 0.5)) +
  geom_hline(yintercept = 0, linetype = 3) +
  ylim(c(-0.2, 0.2)) +
  labs(x = "",
       y = "") +
  facet_wrap(fct_rev(emotion) ~ fct_rev(type), scales = "free") +
  coord_flip() +
  #scale_colour_manual(values = c("grey25", "grey50", "grey75")) +
  scale_color_viridis_d(begin = 0, end = 0.5, direction = -1) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  scale_shape_manual(values = c(17, 16)) +
  theme_nice() +   
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.key.size = unit(1, 'cm'),
        strip.text.x = element_text(size = 8)
    ) +
  guides(color = guide_legend(reverse = TRUE),
         linetype = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

@@

# actual plot
ggplot(pdata_counter_frame, aes(x = outcome, y = estimate, color = correction, shape = correction)) +
  geom_point(size = 1.5, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = lower, ymax = upper, linetype = emotion),
                size = 0.5,
                width = 0.25,
                position = position_dodge(width = 0.5)) +
  geom_hline(yintercept = 0, linetype = 3) +
  ylim(c(-0.2, 0.2)) +
  labs(x = "",
       y = "") +
  facet_wrap(fct_rev(emotion) ~ fct_rev(type), scales = "free") +
  coord_flip() +
  #scale_colour_manual(values = c("grey25", "grey50", "grey75")) +
  scale_color_viridis_d(begin = 0, end = 0.75, direction = -1) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  scale_shape_manual(values = c(15, 16)) +
  theme_nice() +   
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.key.size = unit(1, 'cm'),
        strip.text.x = element_text(size = 8)
  ) +
  guides(color = guide_legend(reverse = TRUE),
         linetype = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))
